---
title: "Auto for GG"
author: " "
date: |
  `r format(Sys.time(), '%B %d, %Y')` 
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: true
    toc_collapse: true
    theme: united
    highlight: zenburn
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load(ggplot2, dplyr, ggthemes, ggpubr, ggcorrplot, rjson, stringr, patchwork, plotly)
```

***
# Data

## Data from 3 sources

```{r}
load("auto.data.Rda")
auto.data$Price <- str_remove_all(auto.data$Price, "[^0-9]*")
auto.data$Price <- ifelse(nchar(auto.data$Price)>4, as.character(as.numeric(auto.data$Price)/420), auto.data$Price)
auto.data$Price <- as.numeric(auto.data$Price)
auto.data$year <- as.numeric(auto.data$year)
auto.data <- filter(auto.data, Price>1500, year > 1995)
#auto.data %>% arrange(Price, desc(year), desc(Milage)) %>% select(Price, year, Milage, everything()) %>% View()
#auto.data %>% select(ID, Date, everything()) %>% View()

auto.data$MM <- paste(str_split(auto.data$Fullname, pattern = "\\s+", simplify = T)[,1],str_split(auto.data$Fullname, pattern = "\\s+", simplify = T)[,2])
auto.data$MM1 <- paste(str_split(auto.data$Fullname, pattern = "\\s+", simplify = T)[,1])
auto.data$mod.year <- paste(cut(auto.data$year, c(1995, 2000, 2010, 2022)), auto.data$MM1)
auto.data$Date <- as.Date(auto.data$Date, format = "%d.%m.%Y")
auto.data %>% DT::datatable()
auto.data$Fullname <- str_remove_all(auto.data$Fullname, "\\s+</span>")
auto.data$Milage <- as.numeric(auto.data$Milage)

auto.data$Milage[auto.data$Milage < 20000] <- NA
```
# Visualization

## Single 

```{r}
p1 <- auto.data %>%
  group_by(MM) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate( Per = round(N/sum(N)*100,1)) %>%
  ggplot() + 
  aes(reorder(MM, N), N, fill = MM, 
                 label = ifelse(N>50, paste0(N," (", round(Per, 1), "%", ")") ,"")) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle(" ")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None") + coord_flip()


p2 <- auto.data %>%
  group_by(MM1) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate( Per = round(N/sum(N)*100,1)) %>%
  ggplot() + 
  aes(reorder(MM1, N), N, fill = MM1, 
                 label = ifelse(N>50, paste0(N," (", round(Per, 1), "%", ")") ,"")) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle(" ")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None") + coord_flip()

plotly::ggplotly(p1)%>%layout(showlegend=FALSE)
plotly::ggplotly(p2)%>%layout(showlegend=FALSE)
```


```{r}
auto.data$Autom <- factor(auto.data$Autom)
levels(auto.data$Autom) <- c(NA,"Automatic", "Manual","Semi-automatic","Automatic", "Manual", "Semi-automatic")
auto.data$Autom[auto.data$Autom==""] <-NA
auto.data$rul[auto.data$rul==""] <-NA
auto.data$gas <- factor(auto.data$gas)
levels(auto.data$gas) <- c(NA, "Diesel", "Diesel",  "Gas"   ,  "Gas/Gasoline" ,"Gasoline"  )

p3 <- auto.data %>%
  group_by(Autom) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate( Per = round(N/sum(N)*100,1)) %>%
  na.omit() %>% 
  ggplot() + 
  aes(reorder(Autom, N), N, fill = Autom, 
                 label = ifelse(N>50, paste0(N," (", round(Per, 1), "%", ")") ,"")) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle("  ")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None")

p3.1 <- auto.data %>%
  group_by(rul) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate( Per = round(N/sum(N)*100,1)) %>%
  na.omit() %>% 
  ggplot() + 
  aes(reorder(rul, N), N, fill = rul, 
                 label = ifelse(N>50, paste0(N," (", round(Per, 1), "%", ")") ,"")) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle(" ")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None")

p3.2 <- auto.data %>%
  group_by(gas) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate( Per = round(N/sum(N)*100,1)) %>%
  na.omit() %>% 
  ggplot() + 
  aes(reorder(gas, N), N, fill = gas, 
                 label = ifelse(N>50, paste0(N," (", round(Per, 1), "%", ")") ,"")) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle(" ")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None")


plotly::ggplotly(p3)%>%layout(showlegend=FALSE)
plotly::ggplotly(p3.1)%>%layout(showlegend=FALSE)
plotly::ggplotly(p3.2)%>%layout(showlegend=FALSE)
```
```{r}
g3.2 <- auto.data %>%
  count( Autom, rul) %>%
  group_by( Autom) %>%
  mutate(Per = n/sum(n) * 100) %>%
  na.omit() %>% 
  ggplot() + 
  aes(reorder( Autom,n), n, fill = rul, 
                 label = n) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab(" ")+ labs(fill ="")+ggtitle(" ")+
 theme_bw() + 
    theme(text = element_text(size=9),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "bottom") + coord_flip()




g3.3 <- auto.data %>%
  count( gas, rul) %>%
  group_by( gas) %>%
  mutate(Per = n/sum(n) * 100) %>%
  na.omit() %>% 
  ggplot() + 
  aes(reorder( gas,n), n, fill = rul, 
                 label = n) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab(" ")+ labs(fill ="")+ggtitle(" ")+
 theme_bw() + 
    theme(text = element_text(size=9),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "bottom") + coord_flip()




plotly::ggplotly(g3.2)
plotly::ggplotly(g3.3)
```

```{r}
p4 <- auto.data %>%
  count( MM1, factor(year)) %>%
  group_by( MM1) %>%
  mutate(Per = n/sum(n) * 100) %>%
  ggplot() + 
  aes(reorder( MM1,n), n, fill = `factor(year)`, 
                 label = n) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab(" ")+ labs(fill ="")+ggtitle(" ")+
 theme_bw() + 
    theme(text = element_text(size=9),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "bottom") + coord_flip()




plotly::ggplotly(p4)
```




```{r}
auto.data$DMonth <- paste(lubridate::year(auto.data$Date), lubridate::quarter(auto.data$Date))
p3.1 <- auto.data %>%
  group_by(DMonth) %>% 
  summarise(N=n()) %>% na.omit() %>%
  mutate(Per = round(N/sum(N)*100,1)) %>%
  na.omit() %>%
  filter(DMonth!="NA NA")%>%
  ggplot() + 
  aes(DMonth, N, fill = DMonth, 
                 label = N) + 
  geom_col(col = "black") +
  geom_text(position=position_stack(0.5), size = 2.5)+
  xlab("")+ labs(fill ="")+ggtitle("Date of the announcement")+
 # scale_fill_manual(values = as.data.frame(yarrr::piratepal("pony"))[,1])+
  theme_bw() + 
    theme(text = element_text(size=8),
          axis.text = element_text(size=8),
          axis.text.x = element_text(angle = 0, hjust = 0.9),
          legend.position = "None")+coord_flip()

plotly::ggplotly(p3.1)%>%layout(showlegend=FALSE)
```

## Mileage and Price

```{r message=FALSE, warning=FALSE}
g1 <- ggplot(data = auto.data,  aes(y=factor(year), x = Price, fill = factor(year))) + 
  geom_boxplot() +  
  stat_summary(fun.x=mean, geom="point", shape=20, size=5, color="white", fill="white") +theme_bw() +
  theme(text = element_text(size=8),
          axis.text.x = element_text(),
          legend.position = "None") +
  ylab("")

auto.data <- filter(auto.data,Milage<500000)
g2 <- ggplot(data = auto.data,  aes(y=factor(year), x = Milage, fill = factor(year))) + 
  geom_boxplot() +  
  stat_summary(fun.x=mean, geom="point", shape=20, size=5, color="white", fill="white") +theme_bw() +
  theme(text = element_text(size=8),
          axis.text.x = element_text(),
          legend.position = "None") +
  ylab("")

g1
g2+ scale_x_continuous(labels = scales::comma)
```

## Choosing the best one 

 Filters

* `!(View %in% c("Coupe","Truck")`
* `!(MM1 %in% c("VAZ|UAZ|GAZ"))`
* `Milage <250000`

```{r}
table(auto.data$View)
auto.data <- auto.data %>% filter(!(View %in% c("Coupe","Truck")) )
auto.data <- auto.data %>% filter(!(str_detect(Fullname, pattern = "VAZ|UAZ|GAZ") ))
auto.data <- auto.data %>% filter(Milage<250000)

g1 <- ggplot(data = auto.data,  aes(y=factor(year), x = Price, color = gas, text = paste(Fullname, "\n", Autom, "\n", rul, "\n", color, "\n", View, "\n", Date, "\n", ID, volume))) + 
  geom_point() +theme_bw() +
  theme(text = element_text(size=8),
          axis.text.x = element_text(),
          legend.position = "None") +
  ylab("")+coord_flip()

g2 <- ggplot(data = auto.data,  aes(y=factor(year), x = Milage, color = gas, text = paste(Fullname, "\n", Autom, "\n", rul, "\n", color, "\n", View, "\n", Date, "\n", ID, volume))) + 
  geom_point() +theme_bw() +
  theme(text = element_text(size=8),
          axis.text.x = element_text(),
          legend.position = "None") +
  ylab("")+coord_flip()

ggplotly(g1)
ggplotly(g2)
```

```{r}
g3 <- ggplot(data = auto.data,  aes(y=Price, x = Milage, color = gas, 
                                    text = paste(Fullname, "\n", Autom, "\n", rul, "\n", color, "\n", View, "\n", Date, "\n", ID, volume)
                                    
                                    )) + 
  geom_point() +theme_bw() +
  theme(text = element_text(size=8),
          axis.text.x = element_text(),
          legend.position = "None") +
  ylab("")+coord_flip()

ggplotly(g3)
```

## Select

```{r}
sel <- auto.data %>% filter(Price<=6500, Milage<110000, year>2001) %>% 
  select(year, Milage, Price, Fullname,Autom, rul, gas, color, View, Date, everything()) %>% arrange(desc(year), Milage, Price, Fullname) 

rownames(sel) <- sel$ID
sel %>% DT::datatable()
```


## Top 5

 1. A24 - Mazda Demio[details](https://autopro.am/car.php?id=28241) 
 
 2. A9 - Nissan Skyline [details](https://autopro.am/car.php?id=30412)
 
 3. A5 - Nissan Tiida[details](https://autopro.am/car.php?id=30840)
 
 4. L62 - Skoda Roomster [details](https://www.list.am/item/17866716	)
 
 5. A17 - Nissan Blue Bird: [details](https://autopro.am/car.php?id=29418)
 
 
### Previous

Mazda 6 - https://www.list.am/item/17935141
Volkswagen Passat - https://www.list.am/item/17924115
Nissan Teana - https://autopro.am/car.php?id=24056
Nissan March 2003 https://autopro.am/car.php?id=4732

 